\section{Timeline}
\label{sec:appA}

\begin{enumerate}
\item \textbf{Add Item 0. Get turnover from Canlas, Cuniff, exercise stuff to know we can fly, can talk to optitrack, and that you have a laptop available with all software planned to be used.}

\item Simulation
\begin{enumerate}
\item Familiarize myself with simulation capabilities.
\begin{enumerate}
\item Test all demos (1 week)
 \item Adapt some variables to see how the simulated results respond (1 week)
\item Upload model of the Crazyflie quadrotor to the simulation to be used for accurate simulation data. (1-3 days) 
\end{enumerate}

\item Create a desired path for the Crazyflies to fly.
\begin{enumerate}
\item Choose 3 different desired flight shapes and adapt simulation code to take them in as the desired flight path for the quadrotor. (1 week)
\item Run simulation tests and error calculations. Debug any issues with simulation. (1-2 weeks)
\item Plot all position, velocity, and accelerations vs. time (both linear and rotational on all 3 axis). (1-2 days)
\end{enumerate}

\item Test hummingbird trajectories in simulation.
\begin{enumerate}
\item Upload hummingbird dive trajectories into simulation. (3 days)
 \item Run simulation and plot position, velocity, and acceleration data vs. time for all 3 axes in both the linear and rotational frames. (2 days)
\item Conduct error calculations between the desired trajectory and the simulated trajectory of the quadrotor. (1 week)
\item Determine acceptable region of error, and determine a maximum theoretical performance for the quadrotor as a measure of how fast the quadrotor is able to complete the maneuver as compared to the hummingbird. (1 week)
\end{enumerate}
\end{enumerate}
 
\item Proof of Concept Demonstration
\begin{enumerate}
\item Purchase new Crazyflie and supporting materials
\begin{enumerate}
\item Create online shopping cart pdf of all materials: Crazyflie, extra blades, extra battery, more OptiTrack markers, etc. (3 days)
\item Create RQ forms and ITPR forms (\textbf{Marcello}\footnote{I've done the first ones as examples for you. You're doing all the others.}) (1 week).
\end{enumerate}

\item Obtain manual control of a Crazyflie with remote control.
\begin{enumerate}
\item Configure Crazyradio and obtain positive connection to the Crazyflie using Crazyflie PC client software. (1-2 days)
\item Connect controller to laptop and configure manual controls to Mode 2 (1 day)
\item Conduct takeoff/landing procedures. (1 day)
\item Fly a rough 3D pattern using manual control. (1 day)
\end{enumerate}

\item Obtain flight data using OptiTrack
\begin{enumerate}
\item Set up OptiTrack system to recognize Crazyflie as a rigid body. (3 days)
\item Run sample code to log flight data. (3 days)
\item Manually fly the Crazyflie and obtain flight data. (3 days)
\item Plot position, velocity, and acceleration data vs. time for all 3 axes in both the linear and rotational frames in \MATLAB. (3 days)
\end{enumerate}

\item Fly the Crazyflie Autonomously
\begin{enumerate}
\item Read about ROS and develop python proficiency (4 months, concurrent)
\item Develop/Utilize currently existing control algorithm architecture to autonomously control the Crazyflie through the input of specified waypoints with associated position, velocity, and (orientation?) information. (1-3 weeks)
\item Execute autonomous control and collect flight data using OptiTrack (1 week)
\item Plot position, velocity, and acceleration data vs. time for all 3 axes in both the linear and rotational frames in \MATLAB. (3 days)
\item Conduct error calculations between the desired trajectory and the actual flight trajectory data collected from the OptiTrack system. (1 week)
\item Present experimental findings (1 month).
\end{enumerate}

\end{enumerate}
\end{enumerate}

Total estimated time to completion: \SI{24}{weeks}.
